Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-06-26 DryDep_supplement.tex
First version of revised model description.

\begin{document}
\clearpage
\setcounter{page}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplement}
%\subsection*{S.1 Aerodynamical resistance}
%\begin{table}[!htbp]
%  \caption{Molecular diffusivity for a gas $i$ given as ration $D_\chem{H_2O}/D_i$, reactivity $f^i_0$, and effective Henry's Law constant $H^i_*$.}
%  \begin{tabular}{lcrr@{$\cdot$}l}
%    \tophline
%    & $D_\chem{H_2O}/D_i$ & $f^i_0$ & \multicolumn{2}{l}{$H^i_*$}\\
%    & & & \multicolumn{2}{l}{(\unit{M\,atm^{-1}})}\\
%    \middlehline
%    \chem{O_3}     & 1.6 & 1.0 & 1 & $10^{-2}$\\
%    \chem{SO_2}    & 1.9 & 0.0 & 1 & $10^5$\\
%    \chem{NO_2}    & 1.6 & 0.1 & 1 & $10^{-2}$\\
%    \chem{H_2O_2}  & 1.4 & 1.0 & 1 & $10^5$\\
%    \chem{HCHO}    & 1.3 & 0.0 & 6 & $10^3$\\
%    \chem{NO}      & 1.3 & 0.0 & 2 & $10^{-3}$\\
%    \chem{CH_3CHO} & 1.6 & 15.0 & \multicolumn{2}{l}{$0$}\\
%    \bottomhline
%  \end{tabular}
  %\belowtable{} % Table Footnotes
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{S.1 Dynamic viscosity of air and quasi-laminar resistance}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity.pdf}
  \caption{Sutherland's law and divergence linear fits with one or two degrees of freedom. The fit $\mu(T) = m\cdot T$ is implemented in the Oslo~CTM3. Despite its strong divergence at lower and higher temperatures, the impact of this choice on the results is negligible.}
\end{figure}
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity_zo_Rb.pdf}
  \caption{Comparison of resulting $z_o$ and $R_b$ for $\mu(T) = m\cdot T$  (left panel) and Sutherland's law (right panel). The example displays the distributions for \chem{H_2O} after one day of model integration for both, rough and calm sea case.}
\end{figure}

@@

%  \belowtable{$^*$: CF -- temperate/boreal coniferous; DF -- temperate/boreal deciduous; NF -- Mediterranean needleleaf; BF -- Mediterranean broadleaf; TC -- temperate crop; MC -- Mediterranean crop; RC -- root crop; SNL -- moorland; GR -- grass; MS -- Mediterranean scrub; WE -- wetlands; TU -- tundra; DE -- desert; W -- water; ICE -- ice.}

@@

%\clearpage
\subsection*{S.2 Latitude dependent vegetation height}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/tree_height.pdf}
  \caption{Extension of the latitude dependent vegetation height from northern hemisphere mid latitudes only to a global description. Example heights are shown for coniferous, deciduous, needleleaf, and broadleaf forests as well as Mediterranean shrub. As reference the original range of EMEP is added.}
\end{figure}

\subsection*{S.3 Temperature dependent greening season (python 2.7)}
{\scriptsize
\begin{verbatim}
#----------------------------------------------------------------------------------
import numpy as np
import pandas as pd
import xarray as xr
#----------------------------------------------------------------------------------
def start_growing_season_fixed(lat, **kwargs):
    '''
    Begin of growing season parameterization adapted from SMOKE-BEIS.
    '''
    bLeap = kwargs.pop('leap', False)
    if (bLeap):
       MAY31 = 152
       NOV1  = 306
       DEC31 = 366
    else:
       MAY31 = 151
       NOV1  = 305
       DEC31 = 365

@@

\subsection*{S.4 De-accumulation of photosynthetic active radiation (PAR) from OpenIFS}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.65cm}]{pictures/PAR_as_is.png}
  \caption{Example output from OpenIFS for January 2nd 2005. PAR is accumulated over the period of one day.}
\end{figure}

@@

\subsection*{S.5 Normalized zonal average ozone dry deposition velocity}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-norm_total_ozone_drydepvelo}
  \caption{Normalized zonal average ozone dry deposition velocity.}
\end{figure}

>>>>

\begin{document}
\clearpage
\setcounter{page}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplement}
\subsection*{S.1 Aerodynamical resistance}
\begin{equation}
  \Psi_m(\zeta) =
  \begin{cases}
   \log(\frac{1+x^2}{2}\cdot(\frac{1+x}{2})^2) - 2\cdot \arctan(x+\frac{\pi}{2}) & \quad \emph{if} \quad -2 < \zeta < 0,\\
   - \beta \cdot \zeta & \quad \emph{if} \quad \zeta \ge 0.
  \end{cases}
  \label{eq:psim}
\end{equation}
\begin{equation}
  \Psi_h(\zeta) =
  \begin{cases}
   2\cdot\log(\frac{1+x^2}{2}) & \quad \emph{if} \quad -2 < \zeta < 0,\\
   - \beta \cdot \zeta & \quad \emph{if} \quad \zeta \ge 0.
  \end{cases}
  \label{eq:psim}
\end{equation}
$x = (1-\gamma\cdot\zeta)^\frac{1}{4}$, $\beta = 4.7$, $\gamma = 15$ (from Cansas experiment).
%\begin{table}[!htbp]
%  \caption{Molecular diffusivity for a gas $i$ given as ration $D_\chem{H_2O}/D_i$, reactivity $f^i_0$, and effective Henry's Law constant $H^i_*$.}
%  \begin{tabular}{lcrr@{$\cdot$}l}
%    \tophline
%    & $D_\chem{H_2O}/D_i$ & $f^i_0$ & \multicolumn{2}{l}{$H^i_*$}\\
%    & & & \multicolumn{2}{l}{(\unit{M\,atm^{-1}})}\\
%    \middlehline
%    \chem{O_3}     & 1.6 & 1.0 & 1 & $10^{-2}$\\
%    \chem{SO_2}    & 1.9 & 0.0 & 1 & $10^5$\\
%    \chem{NO_2}    & 1.6 & 0.1 & 1 & $10^{-2}$\\
%    \chem{H_2O_2}  & 1.4 & 1.0 & 1 & $10^5$\\
%    \chem{HCHO}    & 1.3 & 0.0 & 6 & $10^3$\\
%    \chem{NO}      & 1.3 & 0.0 & 2 & $10^{-3}$\\
%    \chem{CH_3CHO} & 1.6 & 15.0 & \multicolumn{2}{l}{$0$}\\
%    \bottomhline
%  \end{tabular}
  %\belowtable{} % Table Footnotes
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{S.2 Dynamic viscosity of air and quasi-laminar resistance}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity.pdf}
  \caption{Sutherland's law and divergence linear fits with one or two degrees of freedom. The fit $\mu(T) = m\cdot T$ is implemented in the Oslo~CTM3. Despite its strong divergence at lower and higher temperatures, the impact of this choice on the results is negligible.}
\end{figure}
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity_zo_Rb.pdf}
  \caption{Comparison of resulting $z_o$ and $R_b$ for $\mu(T) = m\cdot T$  (left panel) and Sutherland's law (right panel). The example displays the distributions for \chem{H_2O} after one day of model integration for both, rough and calm sea case.}
\end{figure}

@@

%  \belowtable{$^*$: CF -- temperate/boreal coniferous; DF -- temperate/boreal deciduous; NF -- Mediterranean needleleaf; BF -- Mediterranean broadleaf; TC -- temperate crop; MC -- Mediterranean crop; RC -- root crop; SNL -- moorland; GR -- grass; MS -- Mediterranean shrub; WE -- wetlands; TU -- tundra; DE -- desert; W -- water; ICE -- ice.}

@@

%\clearpage
\subsection*{S.3 Latitude dependent vegetation height}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/tree_height.pdf}
  \caption{Extension of the latitude dependent vegetation height from northern hemisphere mid latitudes only to a global description. Example heights are shown for coniferous (CF), deciduous (DF), needleleaf (NF), and broadleaf (BF) forests as well as Mediterranean shrub (MS). As reference the original range of EMEP is added.}
\end{figure}

\subsection*{S.4 Temperature dependent greening season (python 2.7)}
{\scriptsize
\begin{verbatim}
#----------------------------------------------------------------------------------
import numpy as np
import pandas as pd
import xarray as xr
#----------------------------------------------------------------------------------
def start_growing_season_fixed(lat, **kwargs):
    '''
    Begin of growing season parameterization adapted from SMOKE-BEIS.
    '''
    bLeap = kwargs.pop('leap', False)
    if (bLeap):
       MAY31 = 152
       NOV1  = 306
       DEC31 = 366
    else:
       MAY31 = 151
       NOV1  = 305
       DEC31 = 365

@@

\subsection*{S.5 De-accumulation of photosynthetic active radiation (PAR) from OpenIFS}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.65cm}]{pictures/PAR_as_is.png}
  \caption{Example output from OpenIFS for January 2nd 2005. PAR is accumulated over the period of one day.}
\end{figure}

@@

\subsection*{S.6 Normalized zonal average ozone dry deposition velocity}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-norm_total_ozone_drydepvelo}
  \caption{Normalized zonal average ozone dry deposition velocity.}
\end{figure}
